Analysis of celiac disease

### 2019-01-23 5-results-celiac.Rmd
use bigstatsr 0.8

```{r, cache=TRUE}
# Train PLR
system.time(
  logit <- big_spLogReg(X = G, y01.train = y[ind.train], 
                        ind.train = ind.train, 
                        covar.train = obj.svd$u[ind.train, ],
                        ncores = NCORES, alphas = 1)
)
# Get K = 10 predictions/individuals
preds1 <- predict(logit, X = G, ind.row = ind.test, 
                  covar.row = obj.svd$u[ind.test, ])
(nb.pred1 <- sum(rowSums(sapply(logit, function(l) l$beta.X != 0)) > 0))
(aucs1 <- AUC(preds1, target = y[ind.test]))
```

```{r}
(p2 <- plot_density_AUC(preds1))
```

@@

preds2 <- predict(logit2, X = G2, ind.row = ind.test, 
                  covar.row = obj.svd$u[ind.test, ])
(nb.pred2 <- sum(rowSums(sapply(logit2, function(l) l$beta.X != 0)) > 0))
(aucs2 <- AUC(preds2, target = y[ind.test]))
```

```{r}
(p3 <- plot_density_AUC(preds2))
```

@@

```{r, fig.asp=1, fig.width=8}
library(plotROC)
scores_tidy <- tibble(
  d = y[ind.test], 
  "C+T-max" = prs[, which.max(aucs)],
  "PLR"     = preds1,
  "PLR3"    = preds2
) %>%
  gather(key = "Method", value = "Score", -d)

>>>>

```{r, cache=TRUE}
# Train PLR
system.time(
  logit <- big_spLogReg(X = G, y01.train = y[ind.train], 
                        ind.train = ind.train, 
                        covar.train = obj.svd$u[ind.train, ],
                        ncores = NCORES, alphas = 1)
)
pred1 <- predict(logit, X = G, ind.row = ind.test, 
                  covar.row = obj.svd$u[ind.test, ])
(nb.pred1 <- summary(logit, best.only = TRUE)$nb_var)
(aucs1 <- AUC(pred1, target = y[ind.test]))
```

```{r}
(p2 <- plot_density_AUC(pred1))
```

@@

pred2 <- predict(logit2, X = G2, ind.row = ind.test, 
                  covar.row = obj.svd$u[ind.test, ])
(nb.pred2 <- summary(logit2, best.only = TRUE)$nb_var)
(aucs2 <- AUC(pred2, target = y[ind.test]))
```

```{r}
(p3 <- plot_density_AUC(pred2))
```

@@

```{r, fig.asp=1, fig.width=8}
library(plotROC)
scores_tidy <- tibble(
  d = y[ind.test], 
  "C+T-max" = prs[, which.max(aucs)],
  "PLR"     = pred1,
  "PLR3"    = pred2
) %>%
  gather(key = "Method", value = "Score", -d)
